---
title: "Mouse similarity"
author: "James Ashmore"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Setup

Set chunk options:

```{r}
knitr::opts_chunk$set(
  autodep    = TRUE,
  cache      = TRUE,
  cache.lazy = FALSE,
  cache.path = "cache/mouse-similarity.Rmd/",
  dev        = "png",
  error      = FALSE,
  message    = FALSE,
  warning    = FALSE,
  fig.align = "center",
  out.width = '100%'
)
```

Load Bioconductor packages:

```{r}
library(scuttle)
```

Load CRAN packages:

```{r}
library(ggplot2)
library(knitr)
library(pheatmap)
library(reshape2)
library(viridis)
```

Source required functions:

```{r}
source("code/splitByCol.R")
```

Read experiment object:

```{r}
sce <- readRDS("output/mouse-neighbors.rds")
```

Make feature names unique:

```{r}
rownames(sce) <- uniquifyFeatureNames(rowData(sce)$gene_id, rowData(sce)$gene_name)
```

Make sample names unique:

```{r}
colnames(sce) <- sce$cell
```

## Processing

Split experiment object by source annotation:

```{r}
sce <- splitByCol(sce, sce$source)
```

Subset reference data to re-mapped cells:

```{r}
ids <- unique(unlist(sce$query$cell.remapped))

sce$reference <- sce$reference[, ids]
```

## Results {.tabset}

### EHF vs EHF

Setup results table and iterator:

```{r}
res <- split(sce$query$cell, sce$query$sample)

res <- expand.grid(
  A = res$LPMP_EHF,
  B = res$LPMP_EHF,
  stringsAsFactors = FALSE
)

knn <- sce$query$cell.remapped

names(knn) <- sce$query$cell

ind <- seq_len(nrow(res))
```

Calculate number of mutual nearest neighbors:

```{r}
res$intersect <- sapply(ind, function(i) {
  
  v1 <- res[i, "A"]

  v2 <- res[i, "B"]

  n1 <- knn[[v1]]

  n2 <- knn[[v2]]
  
  length(intersect(n1, n2))

})
```

Calculate Jaccard index of mutual nearest neighbors:

```{r}
res$jaccard <- sapply(ind, function(i) {
  
  v1 <- res[i, "A"]

  v2 <- res[i, "B"]

  n1 <- knn[[v1]]

  n2 <- knn[[v2]]
  
  I <- length(intersect(n1, n2))
  
  U <- length(n1) + length(n2) - I
  
  I / U

})
```

Print table of results:

```{r}
DT::datatable(res)
```

Plot heatmap of intersection number:

```{r fig.width = 8, fig.height = 8}
pheatmap(
  mat = acast(res, A ~ B, value.var = "intersect"),
  color = viridis(100),
  breaks = seq(0, 20, length.out = 101),
  border_color = NA,
  show_rownames = TRUE,
  show_colnames = TRUE,
  fontsize = 5
)
```

Plot heatmap of jaccard index:

```{r fig.width = 8, fig.height = 8}
pheatmap(
  mat = acast(res, A ~ B, value.var = "jaccard"),
  color = viridis(100),
  breaks = seq(0, 1, length.out = 101),
  border_color = NA,
  show_rownames = TRUE,
  show_colnames = TRUE,
  fontsize = 5
)
```

### LHF vs LHF

Setup results table and iterator:

```{r}
res <- split(sce$query$cell, sce$query$sample)

res <- expand.grid(
  A = res$LPMP_EHF,
  B = res$LPMP_LHF,
  stringsAsFactors = FALSE
)

knn <- sce$query$cell.remapped

names(knn) <- sce$query$cell

ind <- seq_len(nrow(res))
```

Calculate number of mutual nearest neighbors:

```{r}
res$intersect <- sapply(ind, function(i) {
  
  v1 <- res[i, "A"]

  v2 <- res[i, "B"]

  n1 <- knn[[v1]]

  n2 <- knn[[v2]]
  
  length(intersect(n1, n2))

})
```

Calculate Jaccard index of mutual nearest neighbors:

```{r}
res$jaccard <- sapply(ind, function(i) {
  
  v1 <- res[i, "A"]

  v2 <- res[i, "B"]

  n1 <- knn[[v1]]

  n2 <- knn[[v2]]
  
  I <- length(intersect(n1, n2))
  
  U <- length(n1) + length(n2) - I
  
  I / U

})
```

Print table of results:

```{r}
DT::datatable(res)
```

Plot heatmap of intersection number:

```{r fig.width = 8, fig.height = 8}
pheatmap(
  mat = acast(res, A ~ B, value.var = "intersect"),
  color = viridis(100),
  breaks = seq(0, 20, length.out = 101),
  border_color = NA,
  show_rownames = TRUE,
  show_colnames = TRUE,
  fontsize = 5
)
```

Plot heatmap of jaccard index:

```{r fig.width = 8, fig.height = 8}
pheatmap(
  mat = acast(res, A ~ B, value.var = "jaccard"),
  color = viridis(100),
  breaks = seq(0, 1, length.out = 101),
  border_color = NA,
  show_rownames = TRUE,
  show_colnames = TRUE,
  fontsize = 5
)
```

### EHF vs LHF

Setup results table and iterator:

```{r}
res <- split(sce$query$cell, sce$query$sample)

res <- expand.grid(
  A = res$LPMP_EHF,
  B = res$LPMP_LHF,
  stringsAsFactors = FALSE
)

knn <- sce$query$cell.remapped

names(knn) <- sce$query$cell

ind <- seq_len(nrow(res))
```

Calculate number of mutual nearest neighbors:

```{r}
res$intersect <- sapply(ind, function(i) {
  
  v1 <- res[i, "A"]

  v2 <- res[i, "B"]

  n1 <- knn[[v1]]

  n2 <- knn[[v2]]
  
  length(intersect(n1, n2))

})
```

Calculate Jaccard index of mutual nearest neighbors:

```{r}
res$jaccard <- sapply(ind, function(i) {
  
  v1 <- res[i, "A"]

  v2 <- res[i, "B"]

  n1 <- knn[[v1]]

  n2 <- knn[[v2]]
  
  I <- length(intersect(n1, n2))
  
  U <- length(n1) + length(n2) - I
  
  I / U

})
```

Print table of results:

```{r}
DT::datatable(res)
```

Plot heatmap of intersection number:

```{r fig.width = 8, fig.height = 8}
pheatmap(
  mat = acast(res, A ~ B, value.var = "intersect"),
  color = viridis(100),
  breaks = seq(0, 20, length.out = 101),
  border_color = NA,
  show_rownames = TRUE,
  show_colnames = TRUE,
  fontsize = 5
)
```

Plot heatmap of jaccard index:

```{r fig.width = 8, fig.height = 8}
pheatmap(
  mat = acast(res, A ~ B, value.var = "jaccard"),
  color = viridis(100),
  breaks = seq(0, 1, length.out = 101),
  border_color = NA,
  show_rownames = TRUE,
  show_colnames = TRUE,
  fontsize = 5
)
```

## Summary

### Session

Print session information:

```{r}
sessionInfo()
```
