---
title: "Supervised signaling"
author: "James Ashmore"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Setup

Set chunk options:

```{r}
knitr::opts_chunk$set(
  autodep    = TRUE,
  cache      = TRUE,
  cache.path = "cache/supervised-signaling.Rmd/",
  dev        = "png",
  error      = FALSE,
  message    = FALSE,
  warning    = FALSE
)
```

Import DT options:

```{r}
DT::datatable(matrix())
```

Load Bioconductor packages:

```{r}
library(scuttle)
```

Load CRAN packages:

```{r}
library(circlize)
library(ggplot2)  
library(hues)
library(igraph)
library(patchwork)
```

Load Github packages:

```{r}
library(CellChat)
```

Source user functions:

```{r}
source("code/splitByCol.R")
```

## Data

Read experiment object:

```{r}
sce <- readRDS("output/supervised-analysis.rds")
```

Make feature names unique:

```{r}
rownames(sce) <- uniquifyFeatureNames(ID = rowData(sce)$gene_id, names = rowData(sce)$gene_name)
```

Make cell names unique:

```{r}
colnames(sce) <- seq_len(ncol(sce))
```

Split by batch annotation:

```{r}
sce <- splitByCol(sce, sce$batch)
```

## Processing

Create CellChat object for each batch:

```{r}
fit <- lapply(sce, function(x) {
  
  x$label <- droplevels(x$label)
  
  x <- createCellChat(object = x, group.by = "label")
  
  x@DB <- CellChatDB.mouse
  
  x <- subsetData(x)
  
  x <- identifyOverExpressedGenes(x)
  
  x <- identifyOverExpressedInteractions(x)
  
  x <- projectData(x, PPI.mouse)
  
  x <- computeCommunProb(x)
  
  x <- computeCommunProbPathway(x)
  
  x <- aggregateNet(x)

})
```

Merge CellChat objects:

```{r}
all <- mergeCellChat(fit, add.names = c("Het", "Hom"))
```

## Results

### LR {.tabset}

Compare LR signaling between conditions:

```{r, fig.width = 15, fig.height = 15, results = "asis"}
ids <- levels(all@idents$joint)

for (i in ids) {
  
  cat("####", i, "\n")
  
  p1 <- netVisual_bubble(
    object = all,
    sources.use = i,
    targets.use = ids,
    comparison = c(1, 2),
    remove.isolate = FALSE,
    max.dataset = 1,
    title.name = "Increased signaling in Het",
    angle.x = 45
  )
  
  p2 <- netVisual_bubble(
    object = all,
    sources.use = i,
    targets.use = ids,
    comparison = c(1, 2),
    remove.isolate = FALSE,
    max.dataset = 2,
    title.name = "Increased signaling in Hom",
    angle.x = 45
  )
  
  p0 <- wrap_plots(p1, p2)
  
  print(p0)

  cat("\n\n")
  
}
```

## Summary

### Session

Print session information:

```{r}
sessionInfo()
```
